Arc Blanc: a real time ocean simulation framework

### 2024-11-12 paper.tex
Remove abbreviation that wasn't defined

Another approach related to the dynamics of a ship in water is the calculation of the so-called \emph{Response Amplitude Operator} (RAO), which is expressed using strip theory by Salvesen  \etal (1970) \cite{salvesenShipMotionsSea1970}. Fonseca and Guedes Soares (1998) \cite{fonsecaTimeDomainAnalysisLargeAmplitude1998} improved the method to support more nonlinear effects and large amplitude motions. Varela and Guedes Soares (2011) \cite{varelaInteractiveSimulationShip2011} have used a table of pre-calculated RAO, which are later interpolated to achieve an interactive frame rate.
However, to our knowledge, this type of method is either too expensive for real-time simulation or not general enough because it requires some physical pre-computation based on CFD or experimental data.

>>>>

Another approach related to the dynamics of a ship in water is the calculation of the so-called \emph{Response Amplitude Operator} (RAO), which is expressed using strip theory by Salvesen  \etal (1970) \cite{salvesenShipMotionsSea1970}. Fonseca and Guedes Soares (1998) \cite{fonsecaTimeDomainAnalysisLargeAmplitude1998} improved the method to support more nonlinear effects and large amplitude motions. Varela and Guedes Soares (2011) \cite{varelaInteractiveSimulationShip2011} have used a table of pre-calculated RAO, which are later interpolated to achieve an interactive frame rate.
However, to our knowledge, this type of method is either too expensive for real-time simulation or not general enough because it requires some physical pre-computation based on computational fluid dynamics or experimental data.
